### 2024-10-10 paper.tex
adding image wrapper
fixing especial edition issue
fixing how to cite

\nEspecial{xx}

@@

\englishTitle{Exploring the dynamics of lightning and its thermal effects: Insights from data collection and analysis}

@@

\portugueseTitle{Explorando a dinâmica dos raios e seus efeitos térmicos: Percepções a partir da coleta e análise de dados}

@@

  \authorinfo[]{Nikola Tesla}{},
  \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
  \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
  \authorinfo[0000-0000-0000-0000]{Barbara McClintock}{}

@@

\shortHeaderAuthors{Babbage{\it~et~al.}}

@@

>>>>

\nEspecial{x}

@@

\englishTitle{Exploring the dynamics of lightning and its thermal effects: insights from data collection and analysis}

@@

\portugueseTitle{Explorando a dinâmica dos raios e seus efeitos térmicos: percepções a partir da coleta e análise de dados}

@@

  \authorinfo[]{Nikola Tesla}{}

@@

\shortHeaderAuthors{Babbage{\it~et~al}}

@@

  \boxwrapper{
